---
title: "Iowa Active Voter Summary"
execute:
    echo: false
    warning: false
project:
    type: website
    output-dir: docs
format: 
    html:
        embed-resources: true
---

``` {r}
library(readr)

library(sf)
library(dplyr)
library(reactable)
library(gt)
library(mapview)

```


```{r}
sf_data <- read_rds("../clean_data/registrations_sf_summary.rds") |> 
    select(
        NAME, 
        active_pct_2025, active_pct_2015, active_diff,
        two_party_active_pct_2025, two_party_active_pct_2015, two_party_active_diff,
        rep_active_pct_2025, rep_active_pct_2015, rep_active_diff,
        dem_active_pct_2025, dem_active_pct_2015, dem_active_diff
    )

```


:::{.column-page}

#### Variables

* active_pct: Number of active voters divided by total number of voters

* two_party_active_pct: Sum of Republican active percent and Democratic active percent

* rep_active_pct: Number of Republican active voters divided by total number of voters

* dem_active_pct: Number of Democratic active voters divided by total number of voters

#### Suffixes:

* 2025: Data from January 2025

* 2015: Data from January 2015

* diff: Data from January 2025 minus data from January 2015


```{r}
gt(
    sf_data |> 
        st_drop_geometry()
) |>
    fmt_percent(contains("active"), decimals = 1) |>
    opt_interactive(
        page_size_default = 10,
        page_size_values = c(10, 25, 50, 99),
        use_page_size_select = TRUE,
        use_search = TRUE
    )

```


#### Active Voter Percentages (2025)

Click a county to see all of a county's data.
```{r}

mapview(sf_data, zcol = "active_pct_2025")

mapview(sf_data, zcol = "two_party_active_pct_2025")
```


#### Change in Active % from 2015 to 2025

Negative values increase a percentage point decrease from 2015 to 2025. Click a county to see all of a county's data.
```{r}

mapview(sf_data, zcol = "active_diff")

mapview(sf_data, zcol = "two_party_active_diff")
```

:::